Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Constant and Parameter figure

Using type annotations also allows to statically check for typing errors.
For instance, `Parameter`s can be assigned either a number or a time-dependent expression.
But can also be linked to an outside variable when composing models.
As such, they cannot be used to parametrize the initial conditions of variables,
for which we have to use a `Constant`:

```{python}
from poincare import Constant, Parameter, assign

class Model(System):
    c: Constant = assign(default=1, constant=True)
    # two variables sharing initial condition
    x: Variable = initial(default=c)
    y: Variable = initial(default=c)

    p: Parameter = assign(default=1)
    z: Variable = initial(default=p)  # type error
```

>>>>

Using type annotations also allows to statically check for typing errors.
For instance, `Parameter`s can be assigned either a number or a time-dependent expression.
But can also be linked to an outside variable when composing models.
As such, they cannot be used to parametrize the initial conditions of variables,
for which we have to use a `Constant` (@fig-constant).

::: {#fig-constant layout-nrow=2}
```{python}
# | echo: false
from poincare import Constant, Parameter, assign

```{python}
class Model(System):
    c: Constant = assign(default=1, constant=True)
    x: Variable = initial(default=c)
    y: Variable = initial(default=c)

```{python}
class BadModel(System):
    p: Parameter = assign(default=1)
    z: Variable = initial(default=p)  # type error

Constant and Parameter allow to connect initial conditions and equations, respectively.
Using Parameters as initial conditions raises an error,
and can be flagged by static type checkers.
:::
